% ============================================================
%  MODBUS PROTOCOL — COURSE SYLLABUS / SELL SHEET
%  One-page executive overview for SCADA Hub Training Platform
% ============================================================
\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{palatino}
\usepackage[scaled=0.82]{beramono}
\usepackage[
  top=0.55in, bottom=0.55in,
  left=0.65in, right=0.65in
]{geometry}
\usepackage[dvipsnames,svgnames,x11names]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes.geometric,arrows.meta,calc,backgrounds,fit}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage[most]{tcolorbox}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage[
  colorlinks=true, linkcolor=mblue, urlcolor=mcyan,
  pdftitle={Modbus Protocol — Course Syllabus},
  pdfauthor={}
]{hyperref}
\usepackage{parskip}

% Colors
\definecolor{mblue}{HTML}{1565C0}
\definecolor{mcyan}{HTML}{0097A7}
\definecolor{mnavy}{HTML}{0D2137}
\definecolor{morange}{HTML}{E65100}
\definecolor{mgreen}{HTML}{2E7D32}
\definecolor{maccent}{HTML}{E3F2FD}
\definecolor{mgray}{HTML}{546E7A}

\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

% ── Header ───────────────────────────────────────────────────
\begin{tikzpicture}[remember picture, overlay]
  \fill[mnavy] (current page.north west) rectangle ([yshift=-1.05in]current page.north east);
  \node[anchor=west, text=white, font=\fontsize{22}{26}\bfseries\sffamily]
    at ([xshift=0.65in, yshift=-0.38in]current page.north west) {Modbus Protocol};
  \node[anchor=west, text=mcyan!80, font=\fontsize{11}{13}\sffamily]
    at ([xshift=0.65in, yshift=-0.68in]current page.north west) {Study Guide · Industrial Automation Series · SCADA Hub Training Platform};
  % Chapter count badge
  \node[anchor=east, draw=mcyan, rounded corners=5pt, fill=mblue!50,
        inner sep=6pt, text=white, font=\small\bfseries\sffamily]
    at ([xshift=-0.65in, yshift=-0.38in]current page.north east)
    {12 Chapters · 500+ Questions · PDF Included};
  % Orange accent line
  \draw[morange, line width=2pt]
    ([xshift=0.65in, yshift=-0.88in]current page.north west) --
    ([xshift=3.5in, yshift=-0.88in]current page.north west);
\end{tikzpicture}

\vspace{0.95in}

% ── Two-column layout ────────────────────────────────────────
\begin{minipage}[t]{0.60\textwidth}

{\color{mnavy}\rule{\linewidth}{1.2pt}}
\smallskip

{\small\sffamily\color{mgray}\MakeUppercase{What This Course Teaches}}

\smallskip

Modbus is the first protocol every SCADA engineer encounters and the last one they fully understand. Written in 1979 and still running millions of devices in active service, it underpins more industrial infrastructure than any protocol introduced since. This course teaches Modbus from first principles through field-level troubleshooting — not as an academic exercise, but as the engineering foundation you need before every other protocol makes sense.

\smallskip
{\color{mblue}\rule{\linewidth}{0.6pt}}
\smallskip

{\small\sffamily\color{mgray}\MakeUppercase{Chapter Sequence}}

\setlist[enumerate]{noitemsep, topsep=2pt, leftmargin=*, label=\textcolor{mblue}{\small\bfseries\arabic*.}}
\begin{enumerate}\small
  \item \textbf{Introduction to Modbus} — History, RTU vs.\ ASCII vs.\ TCP, the master/slave model, RS-485 specifications.
  \item \textbf{Data Model} — The four register tables, 0- vs.\ 1-based addressing, data types, packed coil transmission.
  \item \textbf{Function Codes} — FC01–FC23, exception codes, the request/response pair structure.
  \item \textbf{RTU Framing} — Binary encoding, CRC-16 calculation, timing-based frame delimitation.
  \item \textbf{ASCII Mode} — LRC checksum, colon/CRLF delimiters, tradeoffs vs.\ RTU.
  \item \textbf{Modbus TCP} — MBAP header, port 502, transaction IDs, gateway behavior.
  \item \textbf{RS-485 Physical Layer} — Differential signaling, termination, cable length vs.\ baud rate.
  \item \textbf{Data Types \& Scaling} — 32-bit floats, word order, engineering unit conversion.
  \item \textbf{Security} — Attack surface analysis, network segmentation strategy, protocol-aware firewall rules.
  \item \textbf{Troubleshooting} — Exception code diagnosis, timeout analysis, common commissioning failures.
  \item \textbf{Advanced Topics} — Multi-drop timing, gateway configuration, Modbus over satellite/radio.
  \item \textbf{Protocol Lab} — Live exercises: frame construction, CRC verification, Wireshark capture analysis.
\end{enumerate}

\smallskip
{\color{mblue}\rule{\linewidth}{0.6pt}}
\smallskip

{\small\sffamily\color{mgray}\MakeUppercase{The Story}}

\small Modbus is the entry point. Engineers who skip it — or who learned it "on the job" without structure — carry gaps that compound as they move up the stack. An engineer who doesn't understand register addressing will struggle with every integration they touch. An engineer who doesn't understand RTU framing cannot diagnose a serial fault without guessing.

This course closes those gaps in sequence: physical layer → framing → function codes → TCP encapsulation → security → lab. By the end, the engineer can read a raw Modbus frame in hex and tell you what register is being read, from which slave, and whether the response is correct — without opening a manual.

\end{minipage}
\hfill
\begin{minipage}[t]{0.36\textwidth}

% Architecture diagram
\begin{tikzpicture}[
  layer/.style={rectangle, rounded corners=4pt, text centered,
    font=\small\sffamily, inner sep=6pt, minimum width=3.8cm, minimum height=0.7cm},
  arrow/.style={-Stealth, thick, color=mblue!60}
]
\node[layer, fill=mblue!15, draw=mblue] (scada) {SCADA / HMI};
\node[layer, fill=mblue!10, draw=mblue!70, below=6pt of scada] (gateway) {Modbus TCP Gateway};
\node[layer, fill=mnavy!8, draw=mnavy!40, below=6pt of gateway] (rs485) {RS-485 Bus};
\node[layer, fill=morange!10, draw=morange!60, below=4pt of rs485] (plc1) {PLC / RTU \#1};
\node[layer, fill=morange!10, draw=morange!60, below=4pt of plc1] (plc2) {PLC / RTU \#2};
\node[layer, fill=morange!10, draw=morange!60, below=4pt of plc2] (plc3) {Field Device \#N};

\draw[arrow] (scada) -- (gateway);
\draw[arrow] (gateway) -- (rs485);
\draw[arrow] (rs485) -- (plc1);
\draw[arrow] (plc1) -- (plc2);
\draw[arrow] (plc2) -- (plc3);

\node[font=\tiny\sffamily\color{mgray}, right=2pt of scada] {Port 502};
\node[font=\tiny\sffamily\color{mgray}, right=2pt of plc1] {Addr 01};
\node[font=\tiny\sffamily\color{mgray}, right=2pt of plc2] {Addr 02};
\node[font=\tiny\sffamily\color{mgray}, right=2pt of plc3] {Addr \ldots};
\end{tikzpicture}

\vspace{6pt}

% Cert box
\begin{tcolorbox}[
  enhanced, colback=maccent, colframe=mblue, arc=4pt,
  fonttitle=\small\bfseries\sffamily\color{white},
  title=Certification Relevance,
  boxed title style={colback=mblue},
  attach boxed title to top left={yshift=-2mm, xshift=5mm},
  top=8pt, bottom=6pt, left=6pt, right=6pt
]
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*, label=\textcolor{mblue}{$\bullet$}}
\begin{itemize}\small
  \item \textbf{ISA CCST} — Modbus is explicitly tested in the Instrumentation \& Control systems domain.
  \item \textbf{GICSP (GIAC)} — ICS protocol knowledge; Modbus is a core topic in all vendor prep materials.
  \item \textbf{CompTIA CySA+} — ICS/OT protocol awareness tested at associate level.
\end{itemize}
\end{tcolorbox}

\vspace{5pt}

% Next steps box
\begin{tcolorbox}[
  enhanced, colback=morange!8, colframe=morange, arc=4pt,
  fonttitle=\small\bfseries\sffamily\color{white},
  title=Next Steps (Certs),
  boxed title style={colback=morange},
  attach boxed title to top left={yshift=-2mm, xshift=5mm},
  top=8pt, bottom=6pt, left=6pt, right=6pt
]
\begin{enumerate}[noitemsep, topsep=0pt, leftmargin=*, label=\small\textcolor{morange}{\arabic*.}]
  \item \small Complete this course + Wireshark guide for hands-on lab skills.
  \item Study ISA-18.2 and ISA-99 (IEC 62443) standards.
  \item Register at \texttt{isa.org} for CCST; at \texttt{giac.org} for GICSP.
  \item Schedule exam within 90 days of course completion.
\end{enumerate}
\end{tcolorbox}

\vspace{5pt}

% Stats row
\begin{center}
\begin{tikzpicture}
  \foreach \val/\lbl/\col [count=\i] in {
    12/Chapters/mblue,
    500+/Questions/morange,
    3/Levels/mgreen
  }{
    \node[rectangle, rounded corners=3pt, fill=\col!12, draw=\col!40,
          inner sep=5pt, minimum width=1.1cm, font=\sffamily,
          text=\col] at (\i*1.35, 0)
      {\textbf{\val}\\\tiny\color{mgray}\lbl};
  }
\end{tikzpicture}
\end{center}

\end{minipage}

% ── Footer ───────────────────────────────────────────────────
\begin{tikzpicture}[remember picture, overlay]
  \fill[mnavy!90] (current page.south west) rectangle ([yshift=0.32in]current page.south east);
  \node[anchor=west, text=white!70, font=\footnotesize\sffamily]
    at ([xshift=0.65in, yshift=0.16in]current page.south west)
    {SCADA Hub Training Platform · scada-hub.vercel.app · Free access · No account required for study material};
  \node[anchor=east, text=mcyan, font=\footnotesize\bfseries\sffamily]
    at ([xshift=-0.65in, yshift=0.16in]current page.south east)
    {Course 1 of 8};
\end{tikzpicture}

\end{document}
