% ============================================================
%  SEL RTAC — COURSE SYLLABUS / SELL SHEET
% ============================================================
\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{palatino}
\usepackage[scaled=0.82]{beramono}
\usepackage[top=0.55in, bottom=0.55in, left=0.65in, right=0.65in]{geometry}
\usepackage[dvipsnames,svgnames,x11names]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes.geometric,arrows.meta,calc,backgrounds,fit}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage[most]{tcolorbox}
\usepackage[colorlinks=true, linkcolor=rgreen, urlcolor=rcyan,
  pdftitle={SEL RTAC — Course Syllabus}]{hyperref}
\usepackage{parskip}

\definecolor{rgreen}{HTML}{15803D}
\definecolor{rcyan}{HTML}{059669}
\definecolor{rnavy}{HTML}{052E16}
\definecolor{rorange}{HTML}{D97706}
\definecolor{rblue}{HTML}{1D4ED8}
\definecolor{raccent}{HTML}{F0FDF4}
\definecolor{rgray}{HTML}{6B7280}

\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

\begin{tikzpicture}[remember picture, overlay]
  \fill[rnavy] (current page.north west) rectangle ([yshift=-1.05in]current page.north east);
  \node[anchor=west, text=white, font=\fontsize{22}{26}\bfseries\sffamily]
    at ([xshift=0.65in, yshift=-0.38in]current page.north west) {SEL RTAC};
  \node[anchor=west, text=rcyan!80, font=\fontsize{11}{13}\sffamily]
    at ([xshift=0.65in, yshift=-0.68in]current page.north west) {Study Guide · Industrial Automation Series · SCADA Hub Training Platform};
  \node[anchor=east, draw=rcyan, rounded corners=5pt, fill=rgreen!60,
        inner sep=6pt, text=white, font=\small\bfseries\sffamily]
    at ([xshift=-0.65in, yshift=-0.38in]current page.north east)
    {8 Chapters · 160+ Questions · PDF Included};
  \draw[rorange, line width=2pt]
    ([xshift=0.65in, yshift=-0.88in]current page.north west) --
    ([xshift=3.5in, yshift=-0.88in]current page.north west);
\end{tikzpicture}

\vspace{0.95in}

\begin{minipage}[t]{0.60\textwidth}

{\color{rnavy}\rule{\linewidth}{1.2pt}}
\smallskip
{\small\sffamily\color{rgray}\MakeUppercase{What This Course Teaches}}
\smallskip

The SEL Real Time Automation Controller (RTAC) is the platform that ties everything else together. It is a protocol gateway, a data concentrator, a logic engine, and an IEC 61850 interface — all in one ruggedized DIN-rail device. In power utilities and critical infrastructure, the RTAC sits between the field device level and the SCADA master, translating protocols, filtering data, and implementing local automation that must survive communication failures.

Engineers who understand the RTAC can design substation automation architectures, configure protocol mappings between DNP3, Modbus, and IEC 61850, and implement local control logic using ACSELERATOR Architect. This course covers the full stack from hardware commissioning through advanced protocol gateway configuration.

\smallskip
{\color{rgreen}\rule{\linewidth}{0.6pt}}
\smallskip
{\small\sffamily\color{rgray}\MakeUppercase{Chapter Sequence}}

\setlist[enumerate]{noitemsep, topsep=2pt, leftmargin=*, label=\textcolor{rgreen}{\small\bfseries\arabic*.}}
\begin{enumerate}\small
  \item \textbf{RTAC Architecture} — Hardware variants (SEL-3505/3530/3555), I/O modules, communication ports, power requirements, hardware commissioning.
  \item \textbf{ACSELERATOR Architect} — Software environment, project structure, database tags, tag aliasing, revision control.
  \item \textbf{DNP3 Configuration} — DNP3 master and outstation roles, point mapping, event handling, unsolicited reporting configuration.
  \item \textbf{Modbus Gateway} — Modbus TCP server configuration, register mapping from DNP3 points, coil and holding register layout.
  \item \textbf{IEC 61850 Integration} — GOOSE messaging, Sampled Values, MMS client/server, logical node mapping to RTAC tags.
  \item \textbf{Local Logic} — ACSELERATOR logic engine: IEC 61131-3 programs, event-driven automation, failover sequences.
  \item \textbf{Security \& Access Control} — Role-based access, RBAC configuration, serial port security, firmware update procedures.
  \item \textbf{Field Scenarios} — Substation automation case studies: transformer bay control, feeder protection, load shedding automation.
\end{enumerate}

\smallskip
{\color{rgreen}\rule{\linewidth}{0.6pt}}
\smallskip

{\small\sffamily\color{rgray}\MakeUppercase{The Story}}

\small Substation automation is the application domain where every protocol from this curriculum converges. A modern substation communicates via DNP3 to the SCADA master, via IEC 61850 GOOSE between protection relays, via Modbus to legacy meters, and via serial to older RTUs. The RTAC is the device that manages all of that simultaneously.

SEL dominates the power utility automation market in North America. Understanding the RTAC is not optional for engineers working in substations, distribution automation, or grid modernization. This course provides the configuration depth that the SEL documentation provides in six separate manuals — integrated into a learning sequence that connects each feature to the underlying protocol concepts taught in the prior courses.

\end{minipage}
\hfill
\begin{minipage}[t]{0.36\textwidth}

% Gateway architecture diagram
\begin{tikzpicture}[
  blk/.style={rectangle, rounded corners=3pt, draw, fill, text centered,
    font=\small\sffamily, inner sep=5pt, minimum width=3.6cm, minimum height=0.58cm},
  arr/.style={Stealth-Stealth, thick}
]
\node[blk, draw=rblue, fill=rblue!12] (scada) {SCADA Master};
\node[blk, draw=rgreen, fill=rgreen!12, below=10pt of scada] (rtac) {\textbf{SEL RTAC}};
\node[blk, draw=rnavy!60, fill=rnavy!8, below left=10pt and -20pt of rtac, minimum width=1.6cm] (dnp) {DNP3};
\node[blk, draw=rnavy!60, fill=rnavy!8, below right=10pt and -20pt of rtac, minimum width=1.6cm] (61850) {IEC 61850};
\node[blk, draw=rorange!60, fill=rorange!8, below=8pt of dnp, minimum width=1.6cm] (mbx) {Modbus RTU};

\draw[arr, color=rblue!60] (scada) -- node[right, font=\tiny\sffamily]{DNP3/TCP} (rtac);
\draw[arr, color=rgreen!60] (rtac) -- (dnp);
\draw[arr, color=rgreen!60] (rtac) -- (61850);
\draw[arr, color=rorange!60] (dnp) -- (mbx);

\node[font=\tiny\sffamily\color{rgray}, left=2pt of dnp] {Port 20000};
\node[font=\tiny\sffamily\color{rgray}, right=2pt of 61850] {Port 102};
\end{tikzpicture}

\vspace{5pt}

\begin{tcolorbox}[
  enhanced, colback=raccent, colframe=rgreen, arc=4pt,
  fonttitle=\small\bfseries\sffamily\color{white},
  title=Certification Relevance,
  boxed title style={colback=rgreen},
  attach boxed title to top left={yshift=-2mm, xshift=5mm},
  top=8pt, bottom=6pt, left=6pt, right=6pt
]
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*, label=\textcolor{rgreen}{$\bullet$}}
\begin{itemize}\small
  \item \textbf{SEL Certified Engineer} — SEL offers application engineer certification via their training center; RTAC configuration is a core track.
  \item \textbf{GICSP (GIAC)} — Substation automation and IEC 61850 security appear in ICS security certification exams.
  \item \textbf{ISA CCST} — Protocol gateway configuration and field device integration are tested topics.
\end{itemize}
\end{tcolorbox}

\vspace{5pt}

\begin{tcolorbox}[
  enhanced, colback=rorange!8, colframe=rorange, arc=4pt,
  fonttitle=\small\bfseries\sffamily\color{white},
  title=Next Steps (Certs),
  boxed title style={colback=rorange},
  attach boxed title to top left={yshift=-2mm, xshift=5mm},
  top=8pt, bottom=6pt, left=6pt, right=6pt
]
\begin{enumerate}[noitemsep, topsep=0pt, leftmargin=*, label=\small\textcolor{rorange}{\arabic*.}]
  \item \small Complete DNP3 + RTAC guides together for full stack coverage.
  \item Download ACSELERATOR Architect (free from selinc.com) and configure a lab project.
  \item Attend SEL application engineering training (Pullman, WA or regional).
  \item Pursue GICSP for the ICS security credential that pairs with RTAC expertise.
\end{enumerate}
\end{tcolorbox}

\vspace{5pt}

\begin{center}
\begin{tikzpicture}
  \foreach \val/\lbl/\col [count=\i] in {
    8/Chapters/rgreen,
    4/Protocols/rorange,
    160+/Questions/rblue
  }{
    \node[rectangle, rounded corners=3pt, fill=\col!12, draw=\col!40,
          inner sep=5pt, minimum width=1.1cm, font=\sffamily, text=\col] at (\i*1.35, 0)
      {\textbf{\val}\\\tiny\color{rgray}\lbl};
  }
\end{tikzpicture}
\end{center}

\end{minipage}

\begin{tikzpicture}[remember picture, overlay]
  \fill[rnavy!90] (current page.south west) rectangle ([yshift=0.32in]current page.south east);
  \node[anchor=west, text=white!70, font=\footnotesize\sffamily]
    at ([xshift=0.65in, yshift=0.16in]current page.south west)
    {SCADA Hub Training Platform · scada-hub.vercel.app · Free access · No account required for study material};
  \node[anchor=east, text=rcyan, font=\footnotesize\bfseries\sffamily]
    at ([xshift=-0.65in, yshift=0.16in]current page.south east)
    {Course 6 of 8};
\end{tikzpicture}

\end{document}
